Dusty galaxies and the degeneracy between their dust distributions and the attenuation formula

### 2015-09-30 paper.tex
Final mods

The sample, from \citet{overzier11}, contains galaxies that lie roughly on
the low-redshift IRX-$\beta$ relation.  This relation is a blunt instrument we
use to determine whether or not galaxies obey an attenuation formula at UV
wavelengths; \alephuv~is a function of IRX and an attenuation formula relates
\alephuv~to $\beta$.  Since these galaxies lie on the relation, we
expect them to have dust properties that conform with the properties of
the galaxies in the \citet{calzetti00} sample.  We calculate \alephha~and
\alephuv~for each galaxy in the following way.
\begin{itemize}
\item \alephuv~= ($L_{\mathrm{IR}}$/($1.68\times0.16\times
L_{\mathrm{0.16}}$)+1)$^{-1}$.  This is equivalent to \alephuv~= (emergent UV
SFR)/(IR SFR + emergent UV SFR).
%\item \alephuvha~= \alephuv$^{0.33}$.
\item Following the assumptions in \ref{sfrs}: \alephha~=
(emergent H$\alpha$ SFR)/(IR SFR + emergent UV SFR).
\end{itemize}
We use these quantities to find, for the sample, a best-fit power-law index $q$
for the form \alephha~= \alephuv$^{q}$.

@@

The dispersion about the best-fit relation for high-redshift dusty galaxies
is large, yet it is susceptible
to our possibly invalid assumption that a galaxy's instantaneous SFR has,
for at least $10^{8}$ yr, equaled its prolonged SFR.  For example, if most
massive stars formed over 15 Myr instead of 300 Myr, we should multiply
$L_{0.16}$ and $L_{\mathrm{IR}}$ by larger numbers than we do here to derive the
UV and IR SFRs.  The true UV SFR is 57\% higher and the true IR SFR is 63\%
higher \citep{madau14}.  The true UV escape fraction is little different;
because the true total SFR is higher, the true H$\alpha$ escape fraction is
lower.  Fig. \ref{spread} exemplifies the spread of true escape fractions that
could contribute to a given escape fraction.  The spread is imprecise for three
reasons:
\begin{enumerate}
\item \citet{madau14} calculate conversion factors between luminosities and
star formation rates at 0.15$\,\micron$ rather than 0.16$\,\micron$.  They
assume a history of constant star formation rate to get factors as a function
the duration of a star formation episode.
\item \citet{madau14} use the models of \citet{conroy10} to calculate these
conversion factors.  The conversion factor between $L_{\mathrm{IR}}$ and
IR-derived SFR is a function of the UV escape fraction as well as the duration
of the star formation episode: SFR(IR)/$L_{\mathrm{IR}} = \mathrm{function}
[\mathrm{duration}, f_{\mathrm{esc}}(0.16\,\micron)]$.  We calculate the spread
using the conversion factor for a fixed UV escape fraction.
\item The \citet{kennicutt98} conversion factors for $L_{0.16}$ and
$L_{\mathrm{IR}}$ are valid at different durations of the star formation
episode.
\end{enumerate}
Another scenario is that massive stars stopped forming within the last
15 Myr.  Perhaps some of the high-redshift dusty galaxies have
complicated star formation histories; the combined effect of deriving correct
SFRs might lead to lower dispersion.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.5]{spread_hauv_age.eps}
\caption{\label{spread}}
\end{figure}

>>>>

The sample, from \citet{overzier11}, contains galaxies that lie roughly on
the low-redshift IRX-$\beta$ relation (rederived in the same paper).  This
relation is a blunt instrument we
use to determine whether or not galaxies obey an attenuation formula at UV
wavelengths; \alephuv~is a function of IRX and an attenuation formula relates
\alephuv~to $\beta$.  Since these galaxies lie on the relation, we
expect them to have dust properties that conform with the properties of
the galaxies in the \citet{calzetti00} sample.  We calculate \alephha~and
\alephuv~for each galaxy in the following way.
\begin{itemize}
\item \alephuv~= ($L_{\mathrm{IR}}$/($1.68\times0.16\times
L_{\mathrm{0.16}}$)+1)$^{-1}$.  This is equivalent to \alephuv~= (emergent UV
SFR)/(IR SFR + emergent UV SFR).
%\item \alephuvha~= \alephuv$^{0.33}$.
\item Following the assumptions in \ref{sfrs}: \alephha~=
(emergent H$\alpha$ SFR)/(IR SFR + emergent UV SFR).
\end{itemize}
We use these quantities to find, for the sample, a best-fit power-law index $q$
for the form \alephha~= \alephuv$^{q}$.

@@

The dispersion about the best-fit relation for high-redshift dusty galaxies
is large, yet it is susceptible
to our possibly invalid assumption that a galaxy's SFR has been
constant for at least $10^{8}$ yr.  For example, if most
massive stars formed over 15 Myr instead of 300 Myr, we should multiply
$L_{0.16}$ and $L_{\mathrm{IR}}$ by larger numbers than we do here to derive the
UV and IR SFRs.  The true UV SFR is 57\% higher and the true IR SFR is 63\%
higher \citep{madau14}.  The true UV escape fraction is little different;
because the true total SFR is higher, the true H$\alpha$ escape fraction is
lower.  Fig. \ref{spread} exemplifies the spread of true escape fractions that
could contribute to a given escape fraction.  The spread is imprecise for three
reasons:
\begin{enumerate}
\item \citet{madau14} calculate conversion factors between luminosities and
star formation rates at 0.15$\,\micron$ rather than 0.16$\,\micron$.
\item \citet{madau14} use the models of \citet{conroy10} to calculate these
conversion factors.  The conversion factor between $L_{\mathrm{IR}}$ and
IR-derived SFR is a function of the UV escape fraction as well as the duration
of the star formation episode: SFR(IR)/$L_{\mathrm{IR}} = \mathrm{function}
[\mathrm{duration}, f_{\mathrm{esc}}(0.16\,\micron)]$.  We calculate the spread
using the conversion factor for the given UV escape fraction.
\item The \citet{kennicutt98} conversion factors for $L_{0.16}$ and
$L_{\mathrm{IR}}$ are valid at different durations of the star formation
episode.
\end{enumerate}
Another scenario is that massive stars stopped forming within the last
15 Myr.  Perhaps some of the high-redshift dusty galaxies have
complicated star formation histories; the combined effect of deriving correct
SFRs might lead to lower dispersion.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.5]{spread_hauv_age.eps}
\caption{The spread of true escape fractions that could contribute to
a given escape fraction if a galaxy's SFR has been constant for a
duration different from $10^{8}$ yr.  We assign the input
$f_{\mathrm{esc}}$ values to the conversion factors
between luminosity and SFR in \citet{kennicutt98}.  The UV and IR conversion
factors change as the duration of the star formation episode varies \citep{madau14}.
The durations for the points shown here range from $2\times10^{7}$ to
$1.5\times10^{10}$ yr.\label{spread}}
\end{figure}
